Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 Response to reviewers.tex

A comparison to existing commercial applications is also included, but
this seems taken from their commercial brochures; it does not offer
any clues on how they differ from the functionality offered by MUSES.
\end{verbatim}

The reviewer is right, the state of the art in commercial solutions was quite brief and descriptive.
We have addressed this issue on the revised version of the paper,
changing several sections in order to compose a State of the art in
applications similar to MUSES, and going deeper in the features that
can be compared with those of our system.

***COMPLETAR destacando lo que se haya cambiado para que el revisor perciba que el cambio ha sido gordo***

\begin{verbatim}
It is also unclear how this paper differs from previous work by the
same authors (and others), which also aimed to describe the system;
more specifically: 
"Enforcing corporate security policies via computational intelligence
techniques", GECCO Comp '14 Proceedings of the 2014 conference
companion on Genetic and evolutionary computation Pages 1245-1252  
\end{verbatim}

The paper has been improved in a number of ways, making it more
distant with respect to our previous works. Moreover, we have remarked
in ***Section X (Page Y) the contributions of the present work with
respect to the previous ones***

@@

***COMPLETAR UN POCO, JUSTIFICANDO LA IMPORTANCIA DE ESTE TRABAJO***

\begin{verbatim}
In this reviewer's opinion, the authors should wait till they have
results to present. 
\end{verbatim}

@@

>>> The aim of this paper is to present a state of the art... ***COMPLETAR***

\begin{verbatim}
The relationship between the scope of the special issue and the
subjects dealt by MUSES is also unclear
\end{verbatim}

@@

[REF1] A.M. Mora, P. De las Cuevas, J.J. Merelo, S. Zamarripa,
M. Juan, A.I. Esparcia-Alcázar, M. Burvall, H. Arfwedson, and
Z. Hodaie,  MUSES A corporate user-centric system which applies CI
methods. Presented at the TRECK track at ACM-SAC 2014. 
[REF2] A.M. Mora, P. de las Cuevas, J.J. Merelo, S. Zamarripa,
A.I. Esparcia-Alcázar, Enforcing Corporate Security Policies via
Computational Intelligence Techniques. Presented at the SecDef
Workshop at ACM-GECCO 2014. July 2014

Comparing these references with the current article, which includes 21 pages:

- The introduction in page 2 is very similar to the introduction in [REF2]
- Pages 3-4 are the same than section 2 in [REF2]
- Pages 12-15 are strikingly similar to [REF1], even using the same figures.
- Pages 15-19 are a raw copy of [REF2], nearly word by word.
- Pages 19-21 are extremely similar to section 4 in [REF1] and section 5 in [REF2], put together.

\end{verbatim}

The reviewer is right in part, since some of the contents are the same when a system is being described.
We have followed his/her request and changed/improved several parts in the text, namely ***DECIR LAS SECCIONES QUE SE HAYAN CAMBIADO***

\begin{verbatim}
Hence, the only *new* research this reviewer is able to identify is
section 3 (pages 5-11), which includes a very detailed
state-of-the-art of current tools for corporate mobile
security. Unfortunately, this is not really a paper focused on the
state-of-the-art in this field.
\end{verbatim}

@@

>>> We have transformed the paper into a state-of-the-art of systems similar to MUSES.

***COMPLETAR***

\begin{verbatim}
The work is good and based on good ideas, and the fact that it is
already accepted in two conferences proves this. This is why I will
recommended a MAJOR REVIEW of the paper. In mi opinion, the authors
should consider:

a) extending the state-of-the-art section, and converting the paper in
a "state of the art" or tools for corporate mobile security. They
already provide very detailed descriptions of IBM, Samsung, Sophos and
a few other system, but only a hint about WSO2 and Blackphone, which
are identified as the main competitors of MUSES in section 5. In this
case, sections 4 and 5 are not really needed, but a description of
MUSES as another system like the others could be a good idea. 
\end{verbatim}

Following the reviewer's suggestions, we have transformed the paper into a state-of-the-art in tools for corporate mobile security. MUSES has been compared with the existing tools in a more detailed way and the description of the system has been reduced in the same way. 
***DECIR LAS SECCIONES CAMBIADAS***

\begin{verbatim}
b) reducing the length of the state-of-the-art section, currently too
long in my opinion, and adding lots of new information and
descriptions of new work, research and results to the sections 4 and
5. 
\end{verbatim}

@@

>>> ***DECIR QUE HEMOS OPTADO POR LO PRIMERO AL NO HABER SUFICIENTES RESULTADOS SIN PUBLICAR ACTUALMENTE***

\begin{verbatim}
My preferences are for option b). In case the authors are interested,
they will find next specific comments for a major revision of the
work.
\end{verbatim}

\begin{verbatim}
= Specific comments =

According to page 12, line 7 "the user interacts with the devices
(...) through the MUSES graphical interface inside his or her own
context". This is surprising. I have pictured MUSES as a hyper-visor
module but, according to this sentence, MUSES is a GUI that contains
every application the user has access to. I think further
clarification are needed about how the user interacts with his
applications and what this GUI the authors are describing is
exactly. Contexts in this sentence "(situation, connection, status)"
do not match contexts in figure 2 "(social, economical, political)".
\end{verbatim}

@@

>>> ***REESCRIBIR ESTO CORRECTAMENTE***

\begin{verbatim}
Page 13. The first reason to use a client/server architecture is that
the event correlation and self-adaptation processes need a very
powerful machine (a server), but this statement seems not be based on
any real experiment run by the authors or any previous references. In
addition, I find the second reason to user a client/server
architecture quite surprising. Quoting: "there are two clearly
separated parts in the system, namely the users (clients) and the
enterprise (server)" I think this is a very weak justification. I can
identify many other actors in the system: data providers (cloud
system, databases...), other workers in the enterprise (for corporate
applications), the friends of the user (for private applications),
external application providers... Hence, if the "second reason" is of
any real value, MUSES would have a P2P architecture. From my point of
view, the reasons given by the authors are too week and, in any case,
there is not really any necessity to justify 
why MUSES has a client/server architecture.
\end{verbatim}

The reviewer is right. We have rewritten the paragraph justifying the use of a server machine due to its computational power, needed for applying Data Mining and Machine Learning techniques over Big Datasets, and also to centralise the data gathering of the system. We have removed the text explaining the consideration of two parts in the system.

\begin{verbatim}
Page 13, line 45 says all data in MUSES will be encrypted. It is not
clear if the authors mean "the Decision Table and the even logger", or
"all data in the devices, including personal data, contact list,
emails..." If it is the latter, authors should explain how MUSES
enforces this policy. Does it control all applications in the mobile
phone? Does the mobile phone run only white-listed applications? 
\end{verbatim}

@@

>>> ***EXPLICAR ESTO MEJOR***

\begin{verbatim}
Some specific examples about the kind of user activity MUSES monitors
and the kind of actuators MUSES implements will be welcome. As is,
sensors and actuators seem like a general idea and readers will
understand the system better with specific examples.
\end{verbatim}

@@

>>> ***PONER EJEMPLOS DE SENSORES Y MONITORIZACIÓN***

\begin{verbatim}
Page 14, line 47 identifies the MusCRTEP as the core of the MUSES
system and provides two references. Unfortunately, these references
are not the implementation of MusCRTEP but a general definition of
what a decision system does. These references are not really needed
and a much more detailed description of MusCRTEP would be welcome
since even the authors identify this module as the core of the
system. 
\end{verbatim}

The description of the performance of the CRTEP has been extended
and improved, with references to two Project Reports which better fit
to the contents.

\begin{verbatim}
Page 18, lines 20-37 hint about the importance of privacy enhancing
technologies in a system that monitors the activity of the user and
sends this activity to a centralized server to be "anonymously
managed". Further information about how the system manages this
information is needed (does private information ever leaves the
personal devices? Which activity is monitored and collected?), as well
as an explanation about how these data is anonymized. Is it anonymized
at the mobile phone? Or in the server's database? 
\end{verbatim}

### 2015-04-16 Response to reviewers.tex

Comparing these references with the current article, which includes 21 pages:

- The introduction in page 2 is very similar to the introduction in [REF2]
- Pages 3-4 are the same than section 2 in [REF2]
- Pages 12-15 are strikingly similar to [REF1], even using the same figures.
- Pages 15-19 are a raw copy of [REF2], nearly word by word.
- Pages 19-21 are extremely similar to section 4 in [REF1] and section 5 in [REF2], put together.

\end{verbatim}

The reviewer is right in part, since some of the contents are the same when a system is being described.
We have followed his/her request and changed/improved several parts in
the text, namely  \begin{itemize}
\item The background has been corrected and expanded.
\item References to papers mentioned by the reviwers and how they
  compare with the current paper (and situation in the project) have
  been added to the introduction.
\item Many more papers have been reviewed and referenced. The
  reference section has grown by half.
\item BYOD solutions have been compared among themselves, and with
  MUSES (section 5).
\item The paper reflects the current, so far unpublished, state of
  Muses architecture and implementation.

@@

\begin{verbatim}
Hence, the only *new* research this reviewer is able to identify is
section 3 (pages 5-11), which includes a very detailed
state-of-the-art of current tools for corporate mobile
security. Unfortunately, this is not really a paper focused on the
state-of-the-art in this field.
\end{verbatim}

As suggested by the reviewer, we have transformed the paper into a
state-of-the-art of systems that offer functionalities that are
similar to MUSES. The paper has been
almost completely rewritten to reflect the state of the art including
changes from the time the first paper was submitted (Samsung dropping
KNOX, for instance).

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Añadidas alguans anotaciones
Adds references to previous works
Checks what has been done to improve the paper in general and changes with respect to the old version. Closes #12 if @amorag or @unintendedbear do not say anything else.

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Enterprises, and particularly their Chief Security Officers (CSOs),
want to ensure that their Security Policies are complied, but this
goal turned hard to achieve since employees are able to use, or bring
their own devices (in what is known as BYOD, bring your own device) at
work, or at home but for work purposes. As this BYOD philosophy is
adopted by many companies everyday, a number of solutions have arisen
in order to adopt it securely. In this paper, a novel system named
MUSES (Multiplatform Usable Endpoint Security) which should be able 
to adapt Security Policies to a BYOD environment is introduced. MUSES
has been designed to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules. MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
This system, still in development, is compared with the most relevant
solutions offered by other companies to deal with the same issues as
MUSES, remarking the advantages that our system will offer with
respect to them. % What do we do in this paper? Present the
                 % architecture? The prototypes? - JJ
\end{abstract}

@@

Moreover, it has been demonstrated that people are the main hazard regarding the company security \cite{Adams_Users05}, so in this situation, some monitorization and security-aimed applications are arising, aiming to cope with the concept of seamless working experience on different devices. 
This concept is a methodology of work which allows users to start/continue a working session over multiple devices and locations without any significant loss of data. This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since the company's data borders have changed in the last years, so now the users can access significant data from outside the enterprise, and possibly through a non absolutely secure channel.

Thus, this work introduces a novel (still in development) system named MUSES, from Multiplatform Usable Endpoint Security, which is a dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a set of security rules defined as specifications of the Corporate Security Policies, but with the ability of `learning' from the user's past behaviour and adapt the set of rules, or even inferring new ones, in order to deal with potential future security incidents due to the user's. %FERGU: The user's "algo que falta"? o eso hace referencia a su culpa?
Then the system will react, in a non-intrusive way, to the potentially dangerous sequence of actions (events) that he or she is conducting at any time.

To this end MUSES will analyse the users' behaviour by means of Data Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning (ML) methods \cite{MachineLearning_Bishop06}, extracting a set of patterns which will be later processed by means of Computational Intelligence (CI) algorithms, namely Evolutionary Computation methods \cite{EAs_Back96,GP_Koza92}.

@@

This work introduces a self-adaptive user-centric end-to-end system, named MUSES, which is in development (it will be launched next year). The architecture and main features of the system are described, paying special attention to the application of Soft Computing methods in tasks of data analysis, machine learning, and also in the use of evolutionary algorithms to improve the existing set of corporate security rules which leads the system.

@@

\bibliographystyle{elsarticle-num}
\bibliography{review_muses} %geneura-latin1

% Antonio - Poner la bibliografía en fichero .bib

%\begin{thebibliography}{00}

%\bibitem{ids13}
%Sommestad T., Hunstad A.. \emph{Intrusion detection and the role of the system administrator.}, from Swedish Defence Research Agency (FOI), Linköping, Sweden, 2013.

%\bibitem{m2m12}
%NTT DOCOMO, \emph{DOCOMO to Launch Global M2M Platform}, in M2M Magazine, December 2012.
%http://www.machinetomachinemagazine.com/2012/12/05/docomo-to-launch-global-m2m-platform/.

%\bibitem{suites12}
%The Radicati Group Inc., report \emph{Microsoft Office 365 - Analysis and Forecast, 2012-2016}. June 2012.

%\bibitem{Adams_Users05}
%Adams, A. and Sasse, A.:
%\newblock {\em Users are not the enemy}.
%\newblock Security and Usability: Designing Systems That People Can Use.
%  O\'Reilly Associations, 2005.

%\bibitem{cost_adjustment_07}
%Alfaro-Cid, E., Sharman, K. and Esparcia-Alcázar, A.I.:
%\newblock A genetic programming approach for bankruptcy prediction using a
%  highly unbalanced database.
%\newblock In M.~Giacobini, editor, {\em Applications of Evolutionary
%  Computing}, volume 4448 of {\em Lecture Notes in Computer Science}, pages
%  169--178. Springer Berlin Heidelberg, 2007.

%\bibitem{AzurriMDM}
%Azurri Communications.
%\newblock Icon Mobilise.
%\newblock \url{http://www.azzurricommunications.com/~/media/Resources/Brochures/Media/icon_mobilise_brochure_online.ashx}

%\bibitem{SecPolComp12}
%Al-Omari, A., El-Gayar, O., Deokar, A., and Walters, J.: \emph{Security Policy Compliance: User Acceptance Perspective}. 45th Hawaii International
%Conference on System Sciences (pp. 3317-3326). IEEE, 2012.

%\bibitem{BYOD13}
%Bacik, S.: \emph{Security Implications of Bring Your Own Device, IT Consumerization, and Managing User Choices}, in Information Security Management Handbook, Sixth Edition, Volume 7, pp. 133-142, 2013.

%\bibitem{EAs_Back96}
%Back, T.:
%\newblock {\em Evolutionary algorithms in theory and practice}.
%\newblock Oxford University Press, 1996.

%\bibitem{MachineLearning_Bishop06}
%Bishop, C.:
%\newblock {\em Pattern recognition and Machine Learning}.
%\newblock Springer, 2006.

%\bibitem{Blackberry_tool}
%Blackberry.
%\newblock Blackberry balance.
%\newblock \url{http://es.blackberry.com/business/software/blackberry-balance.html}

%\bibitem{Blackphone}
%Blackphone.
%\newblock \url{https://www.blackphone.ch/}

%\bibitem{SecPolComp10}
%Bulgurcu, B., Cavusoglu, H., and Benbasat, I.: \emph{Information security policy compliance: an empirical study of rationality-based beliefs and information security awareness}. MIS Quarterly, 34(3), 523-548. 2010.

%\bibitem{botnet_detection_clustering_09}
%Chang, S. and Daniels, T.E.:
%\newblock P2P botnet detection using behavior clustering \& statistical tests.
%\newblock In {\em Proceedings of the 2nd ACM Workshop on Security and
%  Artificial Intelligence}, AISec '09, pages 23--30, New York, NY, USA, 2009.
%  ACM.

%\bibitem{SecPol09}
%Cresson Wood, C. and Lineman, D.: \emph{Information Security Policies Made Easy Version 11}. Information Shield, Inc. 2009.

%\bibitem{inferring_policies_socialnetworks_09}
%Danezis, G.:
%\newblock Inferring privacy policies for social networking services.
%\newblock In {\em Proceedings of the 2Nd ACM Workshop on Security and
%  Artificial Intelligence}, AISec '09, pages 5--10, New York, NY, USA, 2009.
%  ACM.

%\bibitem{Good_tool}
%Good's Technology.
%\newblock BYOD Solution.
%\newblock
%  \url{http://www1.good.com/secure-mobility-solution/bring-your-own-device.html}

%\bibitem{GAs_Goldberg89}
%Goldberg, D.E.:
%\newblock {\em Genetic Algorithms in search, optimization and machine
%  learning}.
%\newblock Addison Wesley, 1989.

%\bibitem{FeatureSelection_Guyon03}
%Guyon, I.,  and Elisseeff, A.:
%\newblock An introduction to variable and feature selection.
%\newblock {\em J. Mach. Learn. Res.}, 3:1157--1182, 2003.

%\bibitem{PatternMining_Han07}
%Han, J., Cheng, H., Xin, D., and Yan, X.:
%\newblock Frequent pattern mining: Current status and future directions.
%\newblock {\em Data Min. Knowl. Discov.}, 15(1):55--86, 2007.

%\bibitem{SecPolPenalty09}
%Herath, T., and Rao, H.R.: \emph{Protection motivation and deterrence: a framework for security policy compliance in organisations}. European Journal of Information Systems, vol. 18, pp. 106-125, 2009.

%\bibitem{IBM_tool}
%IBM.
%\newblock Hosted mobile device security management.
%\newblock
%\url{http://www-935.ibm.com/services/us/en/it-services/managed-security-services-cloud-computing} \url{ -hosted-mobile-device-security-management.html}

%\bibitem{Clustering_Jain99}
%Jain, A.K., Murty, M.N., and Flynn, P.~J.:
%\newblock Data clustering: A review.
%\newblock {\em ACM Comput. Surv.}, 31(3):264--323, Sept. 1999.

%\bibitem{imbalance_techniques_02}
%Japkowicz, N. and Stephen, S.:
%\newblock The class imbalance problem: A systematic study.
%\newblock {\em Intell. Data Anal.}, 6(5):429--449, Oct. 2002.

%\bibitem{ibm11}
%Kao, I-L.: \emph{IBM Security Services. Securing mobile devices in the business environment}, IBM, 2011.

%\bibitem{feature_selection_anomalies_08}
%Kloft, M., Brefeld, U., D\"{u}essel, P., Gehl, C. and Laskov, P.:
%\newblock Automatic feature selection for anomaly detection.
%\newblock In {\em Proceedings of the 1st ACM Workshop on Workshop on AISec},
%  AISec '08, pages 71--76, New York, NY, USA, 2008. ACM.

%\bibitem{GP_Koza92}
%Koza, J.~R.:
%\newblock {\em Genetic Programming: On the programming of computers by means of
%  natural selection}.
%\newblock MIT Press, Cambridge, MA, 1992.

%\bibitem{EAs_securitycosts-kirta} 
%Kirta, T., and Kivimaab, J.: Optimizing it security costs by evolutionary algorithms. In C. Czosseck and K. Podins, editors, Conference on Cyber Con ict,pages 145-160, CCD COE Publications, 2010.

%\bibitem{DataMining_Lee01}
%Lee, S.J. and Siau, K.:
%\newblock A review of data mining techniques.
%\newblock {\em Industrial Management \& Data Systems}, 101(1):41--46, 2001.

%\bibitem{user_classification_ml_13}
%Leontjeva, A., Goldszmidt, M., Xie, Y., Yu, F. and Abadi, M.:
%\newblock Early security classification of skype users via machine learning.
%\newblock In {\em Proceedings of the 2013 ACM Workshop on Artificial
%  Intelligence and Security}, AISec '13, pages 35--44, New York, NY, USA, 2013.
%  ACM.

%\bibitem{sec_policy_evolution_gp_08}
%Lim, Y.T., Cheng, P.C., Rohatgi, P. and Clark, J.A.:
%\newblock Mls security policy evolution with genetic programming.
%\newblock In {\em Proceedings of the 10th Annual Conference on Genetic and
%  Evolutionary Computation}, GECCO '08, pages 1571--1578, New York, NY, USA,
%  2008. ACM.

%\bibitem{MIT05}
%Lippmann, R.P., Ingols, K.W., Scott, C., Piwowarski, K., Kratkiewicz, K.J., Artz, M., and Cunningham, R.K.: \emph{Evaluating and Strengthening Enterprise
%Network Security Using Attack Graphs}. Project Report IA-2. Lincoln Laboratory, Massachusetts Institute of Technology, October 2005.

%\bibitem{GP_intrusion-lu} Lu, W. and Traore, L.: Detecting new forms of network intrusion using genetic programming. In Proceedings of the 2003 Congress on Evolutionary Computation, pages 2165-2172, 2003.

%\bibitem{EventProcessing_Luckham02}
%Luckham, D.:
%\newblock {\em The Power of Events: An Introduction to Complex Event Processing
%  in Distributed Enterprise Systems}.
%\newblock Addison-Wesley, MA, USA, 2002.

%\bibitem{classification_67}
%MacQueen, J.:
%\newblock Some methods for classification and analysis of multivariate
%  observations.
%\newblock In {\em Proceedings of the fifth Berkeley symposium on mathematical
%  statistics and probability}, volume~1, page~14. California, USA, 1967.

%\bibitem{GA_intrusion-majeed} Majeed, P.G. and Kumar, S. Genetic algorithms in intrusion detection systems: A survey. International Journal of Innovation and Applied Studies, 5(3):233-240, March 2014.

%\bibitem{Opp_Security11}
%Oppliger, R.:
%\newblock Security and privacy in an online world.
%\newblock {\em IEEE Computer}, 44(9):21--22, September 2011.

%\bibitem{android11}
%Orthacker, C., Teufl, P., Kraxberger, S., Lackner, G., Gissing, M., Marsalek, A., Leibetseder, J., and Prevenhueber, O.: \emph{Android Security Permissions - Can We Trust Them?}. MobiSec Session on Smartphone Security, Aalborg 2011.

%\bibitem{BigData_11}
%Ratner, B.:
%\newblock {\em Statistical and Machine-Learning Data Mining: Techniques for
%  Better Predictive Modeling and Analysis of Big Data, Second Edition}.
%\newblock CRC Press, Inc., Boca Raton, FL, USA, 2nd edition, 2011.

%\bibitem{policy_generation_clustering_10}
%Samak, T. and Al-Shaer, E.:
%\newblock Synthetic security policy generation via network traffic clustering.
%\newblock In {\em Proceedings of the 3rd ACM Workshop on Artificial
%  Intelligence and Security}, AISec '10, pages 45--53, New York, NY, USA, 2010.
%  ACM.

%\bibitem{Samsung_tool}
%Samsung KNOX.
%\newblock
%  \url{https://www.samsungknox.com}

%\bibitem{Schu_SecPatterns05}
%Schumacher, M., Fernandez-Buglioni, E., Hybertson, D., Buschmann, F., and
%  Sommerlad, P.:
%\newblock {\em Security Patterns: Integrating Security and Systems
%  Engineering}.
%\newblock John Wiley \& sons, 2005.

%\bibitem{RT2AE_SOTICS13}
%Seigneur, J.-M., Kölndorfer, P., Busch, M., and Hochleitner, C.:
%\newblock A survey of trust and risk metrics for a BYOD mobile working world.
%\newblock In {\em Third International Conference on Social Eco-Informatics
%  (SOTICS 2013)}, page To Appear. Curran Associates Inc., November 2013.

%\bibitem{SecPolComp09}
%Shaw, R.S., Chen, C.C., Harris, A.L., and Huang, H.-J.: \emph{The impact of information richness on information security 
%awareness training effectiveness}. Computers \& Education, vol. 52, pp. 92-100, 2009.

%\bibitem{SecPolComp07}
%Siponen, M., Pahnila, S., and Mahmood, A.: \emph{Employees' adherence to information security policies: an empirical study}. In IFIP International Federation for Information Processing, Volume 232, New Approaches for Security, Privacy and Trust in Complex Environments pp. 133-144, 2007.

%\bibitem{AAI_book_2009}
%Solanas, A. and Martínez-bal, A.:
%\newblock {\em Advances in Artificial Intelligence for Privacy Protection and
%  Security}.
%\newblock World Scientific Publishing Co., Inc., River Edge, NJ, USA, 2009.

%\bibitem{Sophos_tool}
%Sophos.
%\newblock Mobile control.
%\newblock \url{http://www.sophos.com/en-us/products/mobile-control.aspx}
%
%\bibitem{rule_generation_gp_09}
%Suarez-Tangil, G., Palomar, E. Fuentes, J., Blasco, J. and Ribagorda, A.:
%\newblock Automatic rule generation based on genetic programming for event
%  correlation.
%\newblock In l.~Herrero, P.~Gastaldo, R.~Zunino, and E.~Corchado, editors, {\em
%  Computational Intelligence in Security for Information Systems}, volume~63 of
%  {\em Advances in Intelligent and Soft Computing}, pages 127--134. Springer
%  Berlin Heidelberg, 2009.

%\bibitem{risk_reduction_ga_12}
%Tamjidyamcholo, A.:
%\newblock Genetic algorithm approach for risk reduction of information
%  security.
%\newblock {\em International Journal of Cyber-Security and Digital Forensics
%  (IJCSDF)}, 1(1), 2012.

%\bibitem{SurveyEventCorrelation_Tiffany02}
%Tiffany, M.:
%\newblock A survey of event correlation techniques and related topics.
%\newblock Research paper, Georgia Institute of Technology, 2002.

%\bibitem{WorxSDK}
%Citrix.
%\newblock Worx App SDK.
%\newblock \url{http://www.citrix.es/go/worx-app-sdk.html}
%
%\bibitem{WSO2_tool}
%WSO2.
%\newblock Enterprise Mobility Manager.
%\newblock \url{http://wso2.com/products/enterprise-mobility-manager/}

%\bibitem{GA_networksecurity-zarza} 
%Zarza, L., Forné, J., Pegueroles, J.R., and Soriano, M.: Advances in artificial intelligence for privacy protection and security, chapter Genetic algorithms for designing network security protocols, pages 325-358. World Scientific, 2010.
%
%\bibitem{GA_cryptographicprotocols-zarza2} 
%Zarza, L., Pegueroles, J., Soriano, M., and Martínez, R.: Design of cryptographic protocols by means of genetic algorithms techniques. In M. Malek, E. Fernández-Medina, and J. Hernando, editors, SECRYPT, pages 316-319. INSTICC Press, 2006.

%\end{thebibliography}

>>>>

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Enterprises, and particularly their Chief Security Officers (CSOs),
want to ensure that their Security Policies are complied, but this
goal turned hard to achieve since employees are able to use, or bring
their own devices (in what is known as BYOD, bring your own device) at
work, or at home but for work purposes. As this BYOD philosophy is
adopted by many companies everyday, a number of solutions have arisen
in order to adopt it securely. In this paper, a novel system named
MUSES (Multiplatform Usable Endpoint Security) which should be able 
to adapt Security Policies to a BYOD environment is introduced. MUSES
has been designed to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules. MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
This system, which has released its first prototypes this year, is compared with the most relevant
solutions offered by other companies to deal with the same issues as
MUSES, remarking the advantages that our system will offer with
respect to them. % What do we do in this paper? Present the
                 % architecture? The prototypes? - JJ
\end{abstract}

@@

Moreover, it has been demonstrated that people are the main hazard regarding the company security \cite{Adams_Users05}, so in this situation, some monitorization and security-aimed applications are arising, aiming to cope with the concept of seamless working experience on different devices. 
This concept is a methodology of work which allows users to start/continue a working session over multiple devices and locations without any significant loss of data. This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since the company's data borders have changed in the last years, so now the users can access significant data from outside the enterprise, and possibly through a non absolutely secure channel. %Antares - Yo quitaba lo de significant loss of data, ya que significant se repite después.

Thus, this work introduces a recently released (in alpha) system named
MUSES, from Multiplatform Usable Endpoint Security, which is a
dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a
set of security rules defined as specifications of the Corporate
Security Policies, but with the ability of `learning' from the user's
past behaviour and adapt the set of rules, or even inferring new ones,
in order to deal with potential future security incidents due to the
user's. %FERGU: The user's "algo que falta"? o eso hace referencia a
        %su culpa? 
%"lo del usuario", literalmente. Pero mejorquitarlo - JJ
Then the system will react, in a non-intrusive way, to the potentially
dangerous sequence of actions (events) that he or she is conducting at
any time.

To this end MUSES analyses the users' behaviour by means of Data
Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning
(ML) methods \cite{MachineLearning_Bishop06}, extracting a set of
patterns which will be later processed by means of Computational
Intelligence (CI) algorithms, namely Evolutionary Computation methods
\cite{EAs_Back96,GP_Koza92}. The general ideas behind MUSES were
already presented in
\cite{DBLP:conf/sac/MoraCGZJEBAH14,DBLP:conf/gecco/MoraCGZE14}. However,
the implementation was in its early stages when those papers were
submitted. After the release of the first prototypes and additional
work on the data mining techniques used \cite{mora14:urls} we have a
clearer idea of MUSES capabilities and, as such, will be presented in
this paper.

@@

This work introduces a self-adaptive user-centric end-to-end system, named MUSES, which is in development (it will be launched next year). The architecture and main features of the system are described, paying special attention to the application of Soft Computing methods in tasks of data analysis, machine learning, and also in the use of evolutionary algorithms to improve the existing set of corporate security rules which leads the system. %Antares - Yo podrían en lugar de ``next year'' el año, porque el artículo puede ser leído en cualquier momento y es mejor emplear referencias absolutas, ¿no creeis?

@@

\bibliographystyle{elsarticle-num}
\bibliography{review_muses,geneura-latin1}
